%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{enumitem}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Anthony Ling} % Your name
\address{850 Concord St. \\ Pleasanton, CA 94566 \\ 1-925-325-7144 \\ ant1ng@berkeley.edu} 
\address{https://ant1ng2.github.io}

\begin{document}

%----------------------------------------------------------------------------------------
%	CARRIER OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Career Objective}
An enthusiastic Senior in Computer Science major seeking exciting internship opportunities in the field of artificial
intelligence, data science, and computer science in general.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, Berkeley} \hfill {August 2016 - Present} 
\\ Bachelor of Art, Computer Science \hfill{GPA: 3.6}

\end{rSection}

%----------------------------------------------------------------------------------------
%	RELATED COURSEWORK SECTION
%----------------------------------------------------------------------------------------

\begin{rSection2}{Related Coursework}
CS 70: Discrete Math and Probability Theory
\\ CS 170: Eff. Alg. and Intractable Problems
\\ CS 61B: Data Structures
\\ CS 61C: Great Ideas in Computer Architecture
\\ EECS 16A: Designing Info Devices and Systems
\\ CS 188: Intro. to Artificial Intelligence
\\ CS 169: Software Engineering
\\ CS 186: Intro. to Databases
\\ CS 189: Intro. to Machine Learning*
\\ EECS 127: Opt. Models and App.*
\end{rSection2}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & Python, Java, HTML/CSS, Javascript, Markdown, SQL, C\# \\
Web App Frameworks \ & Django, Ruby on Rails, Jekyll \\
Software \& Tools & MS Office, LaTeX, G Suite, Adobe Illustrator, VS Code, Unity \\
Software Development & Test Automation, Docker, Bash Scripting, Git / SVN, Agile / Scrum
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Freddie Mac, McLean}{May 2019-August 2019}{Financial Engineering Intern}{}
\item On-site internship under this government-sponsored enterprise. Created a Web application to view graphs on loaning data. Learned the process of mortgage-backed securities and its role in loans and implemented various aspects such as processes monitoring and data analysis tools.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience} 
\begin{rSubsection}{DataBears, Berkeley}{May 2019-Present}{Content Creator/TA}{}
\item Lead developer of the database lecture for the DataBears DeCal, which included creating a presentation, a lab, and a Gradescope autograder environment.
\end{rSubsection}

\begin{rSubsection}{Education Enrichment Center, Pleasanton}{June 2018-August 2018}{Math Teacher/SAT Content Creator}{}
\item Responsible for teaching adolescents math in preparation for the school year as well as developed a curriculum for SAT practice.
\end{rSubsection}

\begin{rSubsection}{Dept. of Computer Science, UC Berkeley}{2017-2018}{Tutor}{}
\item CS 61A: Structure and Interpretation of Computer Programs, CS 61B: Data Structures
\end{rSubsection}
\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricucular} \itemsep -3pt
President of the Amador Valley Game Design Club in 2016. \\
Publicity Chair of the Berkeley Unit 4 Hall Association in 2016-2017 \\
Member of the GameCrafters in 2018. \\
Programmer/Artist in the Game Design Club in 2019-Present.
\end{rSection}

\begin{rSection}{Personal Traits}
Highly motivated and eager to learn new things. \\
Strong motivational and leadership skills. \\
Ability to work as an individual as well as in group. \\
Hardworking individual who is very passionate in his work. \\
Self-proclaimed hilarious/slightly awkward personality.
\end{rSection}

%-----------------------------------------------------------------------------------------
% References
%-----------------------------------------------------------------------------------------
\begin{rSection}{References}
James Naslund: https://www.linkedin.com/in/jim-naslund-4031093/ \\
Mason Chow: https://www.linkedin.com/in/mason-chow-3502a89a/
\end{rSection}
\end{document}
