%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{enumitem}
\usepackage{url}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Anthony Ling} % Your name
\address{1-925-325-7144 \\ acling2k@gmail.com \\ https://ant1ng2.github.io \\ Pleasanton, CA} 

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, Berkeley} \hfill  
\\ Bachelor of Art, Computer Science \hfill{2016-2020}
\\ Master of Science, Computer Science \hfill {2020-2021}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & CPython, Java, HTML/CSS, Javascript, Markdown, SQL, C\#, C, C++ \\
Libraries & OpenMP, MPI, CUDA, OpenGL, Numpy, Pandas, Matplotlib, PyTorch, Bokeh \\
Web App Frameworks & Django, Ruby on Rails, Jekyll, Flask \\
Software \& Tools & MS Office, LaTeX, G Suite, Adobe Illustrator, Unity \\
Software Development & Test Automation, Docker, Bash Scripting, Git / SVN, Agile / Scrum
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Amazon, Seattle}{August 2021-September 2023}{Software Development Engineer}{} 
    \item Worked as a Backend engineer for the Campaign Management Platform for Amazon Advertising (Performance Advertising). Expert-level experience with AWS services (DynamoDB, Cloudwatch, SWF, CloudFormation, Lambda).
    \item Designed and developed an Error detection and recovery mechanism using CloudFormation and Lambda to redrive failed requests from DynamoDB to PostgresSQL for database synchronization. The databases are used to store Advertising Campaign entities. 
    \item Designed and developed an automation tool to fetch availability dips from metrics, fetch related logs, and generate Service Availability reports using Principal Component Analysis. 
    \item Designed and developed a metric generator to alarm on Campaigns that failed validation workflow, resulting in better response to failures.
    \item Worked on large scale codebase migration to another Campaign Management backend.  Collaborated with multiple clients and stakeholders to migrate their calls.
    \item Worked as buddy support for service clients to add model attributes to Targeting Clauses, guiding the team and reviewing pull requests.
    \item Experience with Amazon oncall and software development process, such as pipeline deployments, code reviews, Agile workflow, DevOps. 
\end{rSubsection}

\begin{rSubsection}{Cadence Design Systems, San Jose}{May 2021-August 2021}{Research Intern}{} 
    \item Researching Bayesian Optimization and its applications in electrical-magnetic modeling. 
    \item Devised novel ways to research and apply similar algorithms and techniques in IC design automation software and flows. 
    \item Design and implement software with modern programming and artificial intelligence packages such as PyTorch and Scikit-Learn.
\end{rSubsection}

\begin{rSubsection}{Freddie Mac, McLean}{May 2019-August 2019}{Financial Engineering Intern}{} 
    \item On-site internship under this government-sponsored enterprise.
    \item Project 1: Developed data visualizations (Heatmaps, Bar charts, 3D) using Python libraries Bokeh and Pandas. The visualization system is used for housing loan risk analysis where feature recognition and correlation analysis are essential part of the algorithms and model development.
    \item Project 2: Developed a Django web application that hosts the visuals of the data models. The web application is designed for direct and interactive access to the data by the users. The visualization is configurable by customizing axises and Django caching is deployed for high performance.
\end{rSubsection}

\end{rSection}

\newpage

\begin{rSection}{Academic Projects}

\begin{rSubsection}{GamesCrafters}{2018-2021}{GamesmanPuzzles, Project Lead}{}
	\item Created the GamesmanPuzzles Project, a simple Python interface to solve abstract Puzzle problems with high performance. Developed under the mentorship of Professor Dan Garcia.
	\item Taught a group of undergraduates the principles of software engineering.
	\item Extended Python with C and explored with multiple optimization techniques (i.e. HashTables, MapReduce) to achieve high performance.
	\item Showcases the results using a Web API through Flask.
\end{rSubsection}

\begin{rSubsubsection}{Member}{}
	\item Member of a group devoted to perfectly solving two-player games aka combinatorial and computational game theory.
	\item Helped implement the Universal Web API to combine game solutions from the multiple GamesCrafters backends (ie GamesmanJava, GamesmanClassic). 
	Specifically, worked on translating chess solutions from the Syzygy endgame tablebases from its public API.
	\item Researched using Decision Trees as a way of compressing key-value pairs into a series of feature decisions (i.e. number of pieces on the board, whether the second piece is an "X" or an "O").
\end{rSubsubsection}

\begin{rSubsection}{Actor Migration for Ray}{2020}{Graduate Class Project}{}
	\item Worked on adding an Actor migration feature for the Ray Python package, the simple, universal API for building distributed applications.
	\item Goal was to increase utilization of resources by moving stateful Actors in Nodes that are not sufficiently utilized and placing them together to increase utilization. Requires migrating state, objects and object relationships. 
	\item Worked on Reference Table (Ownership) migration and Benchmarking.
\end{rSubsection}

\begin{rSubsection}{DataBears, Berkeley}{2019}{Content Creator/TA}{}
    \item Developed content for the SQLite lecture, which included a Jupyter Notebook lab, a Gradescope autograder environment, and a Introduction to Databases presentation.
    \item Content covered relational database, DMS, SQL queries and Pandas interactions.
\end{rSubsection}    

\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience} 
\begin{rSubsection}{Education Enrichment Center, Pleasanton}{June 2018-August 2018}{Math Teacher/SAT Content Creator}{}
\item Responsible for teaching adolescents math in preparation for the school year as well as developed a curriculum for SAT practice.
\end{rSubsection}

\begin{rSubsection}{Dept. of Computer Science, UC Berkeley}{2017-2021}{Tutor}{}
\item CS 61A: Structure and Interpretation of Computer Programs, CS 61B: Data Structures
\end{rSubsection}

\begin{rSubsubsection}{GSI}{}
\item CS 61C: Great Ideas in Computer Architecture
\end{rSubsubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular} \itemsep -3pt
Programmer/Artist in the Game Design Club in 2019. \\
Publicity Chair of the Berkeley Unit 4 Hall Association in 2016-2017. \\
President of the Amador Valley Game Design Club in 2016. \\
Volunteered at a Valley Humane Scoiety from 2012-2016. \\
Member of Amador Valley Swim Team from 2014-2016
\end{rSection}

%
%\begin{rSection}{Personal Traits}
%Highly motivated and eager to learn new things. \\
%Strong motivational and leadership skills. \\
%Ability to work as an individual as well as in group. \\
%Hardworking individual who is very passionate in his work. \\
%Self-proclaimed hilarious/slightly awkward personality.
%\end{rSection}

%-----------------------------------------------------------------------------------------
% References
%-----------------------------------------------------------------------------------------
\begin{rSection}{References}
Suomin Cui: \url{https://www.linkedin.com/in/suomin-cui-2703086} \\
James Naslund: \url{https://www.linkedin.com/in/jim-naslund-4031093/} \\
Mason Chow: \url{https://www.linkedin.com/in/mason-chow-3502a89a/} \\
Dan Garcia: \url{https://people.eecs.berkeley.edu/~ddgarcia/}
\end{rSection}

\begin{rSection}{Miscellaneous}
US Citizen
\end{rSection}
\end{document}
